A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-21 4_method.tex
some lil related work updates

\subsubsection{Voronoi Quadrangulation}
The medial axis of a polygonal shape can be obtained from the Voronoi Diagram (VD) generated on the line segments and vertices of the shape. \cite{lee1982medial}
First we throw away all locations in the Voronoi diagram which fall outside the boundary shape.
We can then obtain the medial axis by further reducing the Voronoi bones connected to a concave corner in the boundary shape.

>>>>

\subsubsection{Voronoi Quadrangulation}
\todo{The Voronoi Quadrangulation has already been described in} \cite{Ding2016a}. Section 2.4 Domain Decomposition.

The medial axis of a polygonal shape can be obtained from the Voronoi Diagram (VD) generated on the line segments and vertices of the shape. \cite{lee1982medial}
First we throw away all locations in the Voronoi diagram which fall outside the boundary shape.
We can then obtain the medial axis by further reducing the Voronoi bones connected to a concave corner in the boundary shape.
